(tentative) Rotational Spectral Unmixing of Exoplanets

### 2016-08-19 paper/main.tex
EPOXI geometry table is inserted

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htp]
\caption{EPOXI Observations}
\begin{center}
\begin{tabular}{cccccc} \hline \hline
\multicolumn{2}{c}{Date} & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\
\multicolumn{2}{c}{Phase} & & & & \\ \hline
\multirow{2}{*}{initial sub-solar} & latitude & & & & \\
& longitude  & & & & \\ \hline 
\multirow{2}{*}{initial sub-observer} & latitude & & & & \\
& longitude & & & & \\ \hline
\end{tabular}
\end{center}
\label{tab:EPOXI}
\end{table*}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htp]
\caption{EPOXI Observations}
\begin{center}
\begin{tabular}{lcccc} \hline \hline
& Equator (equinox) & Equator (solstice) & North & South \\ \hline
Date & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\ 
Phase & $57.7^{\circ }$ & $76.6^{\circ }$ & $85.9^{\circ }$ & $86.4^{\circ }$ \\ 
average sub-solar latitude & $-0.4^{\circ }$ & $22.6^{\circ }$ & $3.0^{\circ }$ & $-4.6^{\circ }$ \\
average sub-observer latitude & $1.6^{\circ }$ & $0.3^{\circ }$ & $61.5^{\circ }$ & $-73.7^{\circ }$  \\
initial sub-solar longitude & $267.6^{\circ }$ & $286.0^{\circ }$ & $296.7^{\circ }$ & $33.2^{\circ }$ \\
initial sub-observer longitude & $210.1^{\circ }$ & $210.5^{\circ }$ & $210.1^{\circ }$ & $300.6^{\circ }$ \\ \hline
\end{tabular}
\end{center}
\label{tab:EPOXI}
\end{table*}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
